### 2024-05-02 Manuscript_Figures.Rmd
Committing R files

---
title: "Manuscript Figures"
output: html_document
date: "2024-03-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(here)
library(tidyverse)
library(terra)
library(tidyterra)
library(ggthemes)
library(ggpattern)
```

## Visualize Burn Plot Pre-Landis

Find a way to neatly show initial communities. Show full landscape and burn plot. For full landscape, perhaps just color it by dominant tree species. Show more information for burn plot.

### Full Landis Run

Read in IC map and IC csv. Find tree species with highest biomass for each MapCode, then add that info to the raster.
```{r}
IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
IC_file <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
IC_dom <- IC_file %>%
  group_by(MapCode,SpeciesName) %>%
  summarize(total_sp_biomass = sum(CohortBiomass)) %>%
  ungroup() %>%
  group_by(MapCode) %>%
  slice_max(total_sp_biomass) %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "Oak spp.",
                                 SpeciesName=="TurkeyOak" ~ "Oak spp.",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Longleaf Pine",
                                "Loblolly Pine",
                                "Slash Pine",
                                "Shortleaf Pine",
                                "Tulip Poplar",
                                "Sweetgum",
                                "Red Maple",
                                "Oak spp."
                              ))) %>%
  mutate(SpeciesID = as.numeric(SpeciesName))
IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_map_dom <- left_join(IC_map_df, IC_dom)
IC_map_rst <- IC_map_dom %>% select(SpeciesID)
mapcodes <- unique(IC_map_dom$SpeciesID)
sp_names <- unique(IC_map_dom$SpeciesName)
IC_levels <- tibble("id"=mapcodes, "levels"=sp_names) %>% drop_na()
IC_map$IC_map_rst <- IC_map_rst
IC_dom_map <- IC_map$IC_map_rst
levels(IC_dom_map) <- IC_levels
```

```{r}
ggplot() +
  geom_spatraster(data=IC_dom_map) +
  scale_fill_colorblind() +
  labs(fill="Dominant Tree Species") +
  theme_bw()
#TODO: Reorder legend, remove NA
```

### Zoom in on burn plot

Look at the dominant tree species
```{r}
bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
  project(crs(IC_dom_map))

ext_new = ext(bp4)
ext_new[1] = ext_new[1]-60
ext_new[2] = ext_new[2]+60
ext_new[3] = ext_new[3]-60
ext_new[4] = ext_new[4]+60
IC_crop_bp4 <- crop(IC_dom_map,ext_new)
```
```{r}
ggplot() +
  geom_spatraster(data=IC_crop_bp4)+
  scale_fill_colorblind()+
  geom_spatvector(data=bp4,fill=NA,linewidth=1)+
  theme_bw()
```

Look at forest types before and after

```{r}
before <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
fire2_dry <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-50.csv"))
fire2_wet <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Wet","community-input-file-50.csv"))
fire5_dry <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire5-Dry","community-input-file-50.csv"))
fire5_wet <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-50.csv"))
before$pre_post <- "Initial Conditions"
fire2_dry$pre_post <- "Fire2-Dry"
fire2_wet$pre_post <- "Fire2-Wet"
fire5_dry$pre_post <- "Fire5-Dry"
fire5_wet$pre_post <- "Fire5-Wet"
before_after <- rbind(before,fire2_dry,fire2_wet,fire5_dry,fire5_wet)
```

```{r}
BA_two_sp <- before_after %>%
  group_by(pre_post, MapCode, SpeciesName) %>%
  slice_max(CohortBiomass) %>%
  ungroup() %>%
  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
                                 SpeciesName=="SlashPine" ~ "Slash Pine",
                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
                                 SpeciesName=="RedMaple" ~ "Red Maple",
                                 SpeciesName=="SweetGum" ~ "Sweetgum",
                                 SpeciesName=="WhiteOak" ~ "White Oak",
                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
  mutate(SpeciesName = factor(SpeciesName,
                              levels = c(
                                "Longleaf Pine",
                                "Loblolly Pine",
                                "Slash Pine",
                                "Shortleaf Pine",
                                "Tulip Poplar",
                                "Sweetgum",
                                "Red Maple",
                                "Oak spp."
                              ))) %>%
  group_by(pre_post,MapCode) %>%
  top_n(2, CohortBiomass) %>%
  arrange(MapCode, desc(CohortBiomass)) %>%
  mutate(rank = row_number()) %>%
  select(-CohortAge, -CohortBiomass) %>%
  pivot_wider(names_from = rank, values_from = SpeciesName) %>%
  rename(Highest_Biomass = `1`, Second_Highest_Biomass = `2`) %>%
  ungroup() %>%
  select(-`3`) %>%
  mutate(forest_type = if_else(
    is.na(Second_Highest_Biomass),
    Highest_Biomass,
    paste0("1. ",Highest_Biomass," 2. ",Second_Highest_Biomass)
    )) %>%
  select(MapCode,forest_type,pre_post) %>%
  mutate(forest_type = factor(forest_type))

forest_types <- unique(BA_two_sp$forest_type)
forest_types <- data.frame("forest_type" = forest_types)
forest_types$FT_ID = as.numeric(row.names(forest_types))
forest_types <- forest_types %>% mutate(forest_type = factor(forest_type))

BA_split <- BA_two_sp %>%
  pivot_wider(names_from = pre_post, values_from = forest_type) %>%
  left_join(forest_types, by=join_by("Initial Conditions"=="forest_type")) %>%
  rename(IC_ID = FT_ID) %>%
  left_join(forest_types, by=join_by("Fire2-Dry"=="forest_type")) %>%
  rename(F2D_ID = FT_ID) %>%
  left_join(forest_types, by=join_by("Fire2-Wet"=="forest_type")) %>%
  rename(F2W_ID = FT_ID) %>%
  left_join(forest_types, by=join_by("Fire5-Dry"=="forest_type")) %>%
  rename(F5D_ID = FT_ID) %>%
  left_join(forest_types, by=join_by("Fire5-Wet"=="forest_type")) %>%
  rename(F5W_ID = FT_ID) %>%
  mutate(IC_ID = as.numeric(IC_ID),
         F2D_ID = as.numeric(F2D_ID),
         F2W_ID = as.numeric(F2W_ID),
         F5D_ID = as.numeric(F5D_ID),
         F5W_ID = as.numeric(F5W_ID))

IC_map_df <- as.data.frame(IC_map) %>%
  rename(MapCode = IC_Map_FortBragg)
IC_df <- BA_split %>% select(MapCode,IC_ID)
F2D_df <- BA_split %>% select(MapCode,F2D_ID)
F2W_df <- BA_split %>% select(MapCode,F2W_ID)
F5D_df <- BA_split %>% select(MapCode,F5D_ID)
F5W_df <- BA_split %>% select(MapCode,F5W_ID)
Initial_map <- left_join(IC_map_df, IC_df)
F2D_map <- left_join(IC_map_df, F2D_df)
F2W_map <- left_join(IC_map_df, F2W_df)
F5D_map <- left_join(IC_map_df, F5D_df)
F5W_map <- left_join(IC_map_df, F5W_df)
IC_rst <- Initial_map %>% select(IC_ID)
F2D_rst <- F2D_map %>% select(F2D_ID)
F2W_rst <- F2W_map %>% select(F2W_ID)
F5D_rst <- F5D_map %>% select(F5D_ID)
F5W_rst <- F5W_map %>% select(F5W_ID)

Initial_map$`Initial Conditions` <- IC_rst
IC_all <- Initial_map$`Initial Conditions`
Initial_map$`Fire2-Dry` <- F2D_rst
Initial_map$`Fire2-Wet` <- F2W_rst
Initial_map$`Fire5-Dry` <- F5D_rst
Initial_map$`Fire5-Wet` <- F5W_rst
F2D_all <- Initial_map$`Fire2-Dry`
F2W_all <- Initial_map$`Fire2-Wet`
F5D_all <- Initial_map$`Fire5-Dry`
F5W_all <- Initial_map$`Fire5-Wet`
levels(IC_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F2W_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5D_all) <- forest_types %>% select(FT_ID, forest_type)
levels(F5W_all) <- forest_types %>% select(FT_ID, forest_type)
before_after_all <- c(IC_all,F2D_all,F2W_all,F5D_all,F5W_all)
names(before_after_all) <- c("Initial Conditions","Fire2-Dry","Fire2-Wet","Fire5-Dry","Fire5-Wet")
```

```{r}
before_after_plot <- crop(before_after_all, ext_new)
my_colors = c(colorblind_pal()(8),"gray75")
ggplot() +
  geom_spatraster(data=before_after_plot) +
  facet_wrap(~lyr) +
  geom_spatvector(data=bp4, fill=NA, linewidth=1) +
  scale_fill_manual(values=my_colors, na.value = "transparent") +
  labs(fill="Most abundant tree\nspecies by biomass") +
  theme_bw() +
  theme(axis.text = element_blank(),
        axis.ticks = element_blank())
```

### Plot changes in biomass and age distributions

```{r}
before_after %>%
  group_by(pre_post, MapCode, SpeciesName) %>%
  summarize(TotalBiomass = sum(CohortBiomass)) %>%
  ggplot() +
  geom_bar(aes(x=SpeciesName,y=TotalBiomass,fill=pre_post),stat = "identity", position = position_dodge()) +
  scale_fill_colorblind() +
  theme_bw()
```
```{r}
before_after %>%
  ggplot() +
  geom_boxplot(aes(x=SpeciesName,y=CohortAge,color=pre_post), outlier.shape = 1) + 
  scale_color_colorblind() +
  theme_bw()
```

## Visualize Treelists

```{r}
treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run","Treelist_postlandis_cycle0.csv"))

treelist %>%
  ggplot() +
  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=1) +
  theme_bw()
#TODO: Just do a single mapcode
```

### 2024-05-02 analyze_data.R

@@ -1,0 +1,158 @@
+library(tidyverse)
+library(here)
+library(GGally)
+library(terra)
+library(ggthemes)
+library(tidyterra)
+
+dat <- read.csv(here("all_data.csv"))
+
+dat_summ <- dat %>%
+  group_by(Run) %>%
+  summarize(total_mass_burnt = sum(mass_burnt_pct)/n(),
+            total_surf_cons = sum(surface_consumption, na.rm=T),
+            total_surf_cons_pct = sum(surface_consumption_pct, na.rm=T)/n(),
+            total_canopy_cons = sum(canopy_consumption, na.rm=T),
+            total_canopy_cons_pct = sum(canopy_consumption_pct, na.rm=T)/n(),
+            average_max_power = mean(max_power[max_power > 0], na.rm=T),
+            average_res_time_power = mean(residence_time_power[residence_time_power > 0], na.rm=T),
+            average_res_time_cons = mean(residence_time_consumption[residence_time_consumption > 0], na.rm=T),
+            average_max_react_rate = mean(max_reaction_rate[max_reaction_rate > 0], na.rm=T)) %>%
+  pivot_longer(cols = 2:10,
+               names_to = "variable",
+               values_to = "value")
+
+dat_sd <- dat %>%
+  group_by(Run) %>%
+  summarize(average_max_power = sd(max_power[max_power > 0], na.rm=T),
+            average_res_time_power = sd(residence_time_power[residence_time_power > 0], na.rm=T)) %>%
+  pivot_longer(cols = 2:3,
+               names_to = "variable",
+               values_to = "sd")
+
+dat_summ_sd <- left_join(dat_summ, dat_sd, by = join_by(Run,variable))
+
+dat_summ_sd$Rotation <- rep(NA, nrow(dat_summ_sd))
+dat_summ_sd$Climate <- rep(NA, nrow(dat_summ_sd))
+for(i in 1:nrow(dat_summ_sd)){
+  dat_summ_sd$Rotation[i] <- strsplit(dat_summ_sd$Run[i],"-")[[1]][1]
+  dat_summ_sd$Climate[i] <- strsplit(dat_summ_sd$Run[i],"-")[[1]][2]
+}
+
+dat_summ_clean <- dat_summ_sd %>%
+  select(Rotation, Climate, variable, value, sd) %>%
+  filter(variable %in% c("total_surf_cons_pct",
[…]

### 2024-05-02 qf_outputs_to_dataframe.R

@@ -1,0 +1,61 @@
+library(here)
+library(terra)
+library(tidyverse)
+library(tidyterra)
+
+#### DEFINE FUNCTIONS ####
+
+output_to_rst <- function(output, out_arr, plot_bounds){
+  out_mat <- as.matrix(out_arr)
+  out_rst <- rast(nrow = dim(out_mat)[1],
+                  ncol = dim(out_mat)[2],
+                  crs = crs(plot_bounds),
+                  extent = ext(plot_bounds),
+                  vals = out_mat,
+                  names = output)
+  out_rst <- flip(out_rst, direction="vertical")
+  return(out_rst)
+}
+
+#### ASSEMBLE DATASET ####
+runs <- c("Fire2-Dry","Fire5-Dry","Fire2-Wet","Fire5-Wet")
+outputs <- c("mass_burnt_pct",
+             "surface_consumption",
+             "surface_consumption_pct",
+             "canopy_consumption",
+             "canopy_consumption_pct",
+             "max_power",
+             "residence_time_power",
+             "residence_time_consumption",
+             "max_reaction_rate")
+
+burn_domain <- vect(here("1.LANDIS-MODEL",
+                         "Shapefiles",
+                         "burn_domain.shp"))
+burn_plot <- vect(here("1.LANDIS-MODEL",
+                         "Shapefiles",
+                         "burn_plot.shp"))
+
+for(run in runs){
+  run_df = data.frame("Run" = rep(run,90000))
+  for(output in outputs){
+    out_arr <- read.table(here("7.QUICFIRE-MODEL",
+                               "projects", 
+                               run,
+                               "Arrays",
+                               paste0(output,".txt")))
+    out_rst <- output_to_rst(output, out_arr, burn_domain)
+    writeRaster(out_rst, here(paste0(run,"_",output,".tif")), overwrite=T)
+    out_rst <- crop(out_rst, burn_plot)
+    out_list <- as.vector(values(out_rst))
+    out_df <- data.frame(output = out_list)
+    run_df <- cbind(run_df, out_df)
+    names(run_df)[length(names(run_df))] <- output
+  }
+  assign(paste0(run,"_df"),run_df)
+}
+
+
+
+all_data <- bind_rows(`Fire2-Dry_df`, `Fire2-Wet_df`, `Fire5-Dry_df`, `Fire5-Wet_df`)
+write.csv(all_data, here("all_data.csv"), row.names = F)

### 2024-05-06 Manuscript_Figures.Rmd
Visualize treelist in four mapcodes

@@
 F5W_df <- BA_split %>% select(MapCode,F5W_ID)
+
 Initial_map <- left_join(IC_map_df, IC_df)
@@
 F5W_map <- left_join(IC_map_df, F5W_df)
+
 IC_rst <- Initial_map %>% select(IC_ID)
@@
 
-Initial_map$`Initial Conditions` <- IC_rst
-IC_all <- Initial_map$`Initial Conditions`
-Initial_map$`Fire2-Dry` <- F2D_rst
-Initial_map$`Fire2-Wet` <- F2W_rst
-Initial_map$`Fire5-Dry` <- F5D_rst
-Initial_map$`Fire5-Wet` <- F5W_rst
-F2D_all <- Initial_map$`Fire2-Dry`
-F2W_all <- Initial_map$`Fire2-Wet`
-F5D_all <- Initial_map$`Fire5-Dry`
-F5W_all <- Initial_map$`Fire5-Wet`
+IC_map$`Initial Conditions` <- IC_rst
+IC_map$`Fire2-Dry` <- F2D_rst
+IC_map$`Fire2-Wet` <- F2W_rst
+IC_map$`Fire5-Dry` <- F5D_rst
+IC_map$`Fire5-Wet` <- F5W_rst
+
+IC_all <- IC_map$`Initial Conditions`
+F2D_all <- IC_map$`Fire2-Dry`
+F2W_all <- IC_map$`Fire2-Wet`
+F5D_all <- IC_map$`Fire5-Dry`
+F5W_all <- IC_map$`Fire5-Wet`
+
 levels(IC_all) <- forest_types %>% select(FT_ID, forest_type)
@@
 ```{r}
-treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run","Treelist_postlandis_cycle0.csv"))
+treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","Treelist_postlandis_cycle0.csv"))
+set.seed = 14
+sample_mapcode <- sample(unique(treelist$MapCode),1)
+mapcode <- treelist %>% filter(MapCode == sample_mapcode)
+mapcodes <- treelist %>%
+  filter((X>=100 & X<=300) & (Y>=500 & Y<=700))
 
-treelist %>%
+mapcodes %>%
   ggplot() +
-  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=1) +
+  geom_hline(yintercept = 600, linetype = "dashed") +
+  geom_vline(xintercept = 200, linetype = "dashed") +
+  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
+  scale_color_colorblind() +
+  coord_equal() +
+  labs(X = "X (m)",
+       Y = "Y (m)",
+       color = "Species") +
   theme_bw()
-#TODO: Just do a single mapcode
+#TODO: Replace species codes with species names
 ```

### 2024-05-29 Manuscript_Figures.Rmd
Update example mapcode figure

@@
 library(ggpattern)
+library(sf)
 ```
@@
 
-mapcodes %>%
-  ggplot() +
+mapcodes_vect <- vect(mapcodes, geom=c("X", "Y"), crs="", keepgeom=FALSE)
+
+tree_polys <- list()
+for(i in 1:nrow(mapcodes_vect)){
+  tree_i <- mapcodes_vect[i,]
+  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
+  tree_polys[[i]] <- buffer_i
+}
+mapcodes_poly <- vect(tree_polys)
+writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
+mapcodes_poly <- arrange(mapcodes_poly, CD_m)
+
+example_mapcode <- ggplot() +
   geom_hline(yintercept = 600, linetype = "dashed") +
   geom_vline(xintercept = 200, linetype = "dashed") +
-  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
+  geom_spatvector(data=mapcodes_poly, aes(fill=SPECIES_SYMBOL, color=SPECIES_SYMBOL), alpha=0.7) +
+  scale_fill_colorblind() +
   scale_color_colorblind() +
-  coord_equal() +
-  labs(X = "X (m)",
-       Y = "Y (m)",
-       color = "Species") +
+  labs(x = "X (m)",
+       y = "Y (m)",
+       fill = "Species",
+       color="Species") +
   theme_bw()
+example_mapcode
+ggsave("example_mapcode.jpg",path = here("Plots"))
+
 #TODO: Replace species codes with species names

### 2024-05-29 Manuscript_Figures.Rmd
Create stacked bar chart of biomass

--- 2024-05-06 Manuscript_Figures.Rmd
@@
 
+### Stacked bar chart of species composition in burn plot
+```{r}
+bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
+BA_plot <- before_after %>% 
+  filter(MapCode %in% bp_mapcodes) %>%
+  group_by(pre_post, SpeciesName) %>%
+  summarize(CohortAge_Avg = mean(CohortAge),
+            CohortBiomass_Sum = sum(CohortBiomass)) %>%
+  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
+                                                "Fire2-Dry",
+                                                "Fire2-Wet",
+                                                "Fire5-Dry",
+                                                "Fire5-Wet"))) %>%
+  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
+                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
+                                 SpeciesName=="SlashPine" ~ "Slash Pine",
+                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
+                                 SpeciesName=="RedMaple" ~ "Red Maple",
+                                 SpeciesName=="SweetGum" ~ "Sweetgum",
+                                 SpeciesName=="WhiteOak" ~ "White Oak",
+                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
+                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "White Oak",
+                                "Turkey Oak",
+                                "Red Maple",
+                                "Sweetgum",
+                                "Tulip Poplar",
+                                "Shortleaf Pine",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine"
+                              )))
+
+stacked_barchart <- BA_plot %>%
+  ggplot() +
+  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
+  scale_fill_colorblind() +
+  labs(x="LANDIS Run",
+       y="Total Biomass (kg)",
+       fill="Species") +
+  theme_bw()
+stacked_barchart
+
+ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
+```
+
 ### Plot changes in biomass and age distributions
@@
 
-mapcodes %>%
-  ggplot() +
+mapcodes_vect <- vect(mapcodes, geom=c("X", "Y"), crs="", keepgeom=FALSE)
+
+tree_polys <- list()
+for(i in 1:nrow(mapcodes_vect)){
+  tree_i <- mapcodes_vect[i,]
+  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
+  tree_polys[[i]] <- buffer_i
+}
+mapcodes_poly <- vect(tree_polys)
+writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
+mapcodes_poly <- mapcodes_poly %>%
+  arrange(CD_m) %>%
+  mutate(SpeciesName = case_when(SPECIES_SYMBOL=="PITA" ~ "Loblolly Pine",
+                                 SPECIES_SYMBOL=="PIPA2" ~ "Longleaf Pine",
+                                 SPECIES_SYMBOL=="PIEL" ~ "Slash Pine",
+                                 SPECIES_SYMBOL=="LIST2" ~ "Tulip Poplar",
+                                 SPECIES_SYMBOL=="ACRU" ~ "Red Maple",
+                                 TRUE ~ "Other")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "Other",
+                                "Red Maple",
+                                "Tulip Poplar",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine"
+                              )))
+
+new_colors <- colorblind_pal()(8)[c(1,2,4,5,6)]
+example_mapcode <- ggplot() +
   geom_hline(yintercept = 600, linetype = "dashed") +
   geom_vline(xintercept = 200, linetype = "dashed") +
-  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
-  scale_color_colorblind() +
-  coord_equal() +
-  labs(X = "X (m)",
-       Y = "Y (m)",
-       color = "Species") +
+  geom_spatvector(data=mapcodes_poly, aes(fill=SpeciesName, color=SpeciesName), alpha=0.7) +
+  scale_fill_manual(values = new_colors) +
+  scale_color_manual(values = new_colors) +
+  labs(x = "X (m)",
+       y = "Y (m)",
+       fill = "Species",
+       color="Species") +
   theme_bw()
+example_mapcode
+ggsave("example_mapcode.jpg",path = here("Plots"))
+
 #TODO: Replace species codes with species names

### 2024-05-29 Manuscript_Figures.Rmd
Consistent color scheme

--- 2024-05-06 Manuscript_Figures.Rmd
@@
 IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
+FB_shp <- vect(here("FtBraggBoundary","FtBraggBoundary.shp"))
+FB_shp <- project(FB_shp, IC_map)
+FB_shp <- crop(FB_shp, IC_map)
+
 IC_file <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
@@
                               levels = c(
-                                "Longleaf Pine",
-                                "Loblolly Pine",
-                                "Slash Pine",
-                                "Shortleaf Pine",
-                                "Tulip Poplar",
+                                "Oak spp.",
                                 "Sweetgum",
                                 "Red Maple",
-                                "Oak spp."
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine",
+                                "Shortleaf Pine",
+                                "Tulip Poplar"
                               ))) %>%
@@
   rename(MapCode = IC_Map_FortBragg)
-IC_map_dom <- left_join(IC_map_df, IC_dom)
+IC_map_dom <- left_join(IC_map_df, IC_dom) %>%
+  mutate(SpeciesName = case_when(MapCode %in% c(0,1) ~ "Non-Forest",
+                                 TRUE ~ SpeciesName)) %>%
+  mutate(SpeciesID = if_else(SpeciesName=="Non-Forest",9,SpeciesID))
+
+sp_names <- c(
+  "Sweetgum",
+  "Red Maple",
+  "Oak spp.",
+  "Slash Pine",
+  "Loblolly Pine",
+  "Longleaf Pine",
+  "Shortleaf Pine",
+  "Tulip Poplar",
+  "Non-Forest"
+)
+
 IC_map_rst <- IC_map_dom %>% select(SpeciesID)
-mapcodes <- unique(IC_map_dom$SpeciesID)
-sp_names <- unique(IC_map_dom$SpeciesName)
-IC_levels <- tibble("id"=mapcodes, "levels"=sp_names) %>% drop_na()
 IC_map$IC_map_rst <- IC_map_rst
 IC_dom_map <- IC_map$IC_map_rst
-levels(IC_dom_map) <- IC_levels
+IC_dom_map <- IC_dom_map %>% mutate(IC_map_rst = factor(IC_map_rst, labels = sp_names))
+IC_dom_map <- mask(IC_dom_map, FB_shp)
 ```
@@
 ```{r}
+map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
 ggplot() +
   geom_spatraster(data=IC_dom_map) +
-  scale_fill_colorblind() +
+  scale_fill_manual(values=map_colors, na.value = NA) +
   labs(fill="Dominant Tree Species") +
   theme_bw()
-#TODO: Reorder legend, remove NA
+ggsave("IC_map.jpg", path=here("Plots"), width = 10, height = 5)
 ```
@@
 
+### Stacked bar chart of species composition in burn plot
+```{r}
+bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
+BA_plot <- before_after %>% 
+  filter(MapCode %in% bp_mapcodes) %>%
+  group_by(pre_post, SpeciesName) %>%
+  summarize(CohortAge_Avg = mean(CohortAge),
+            CohortBiomass_Sum = sum(CohortBiomass)) %>%
+  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
+                                                "Fire2-Dry",
+                                                "Fire2-Wet",
+                                                "Fire5-Dry",
+                                                "Fire5-Wet"))) %>%
+  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
+                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
+                                 SpeciesName=="SlashPine" ~ "Slash Pine",
+                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
+                                 SpeciesName=="RedMaple" ~ "Red Maple",
+                                 SpeciesName=="SweetGum" ~ "Sweetgum",
+                                 SpeciesName=="WhiteOak" ~ "White Oak",
+                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
+                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "White Oak",
+                                "Turkey Oak",
+                                "Sweetgum",
+                                "Red Maple",
+                                "Tulip Poplar",
+                                "Shortleaf Pine",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine"
+                              )))
+
+bar_colors <- colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)]
+stacked_barchart <- BA_plot %>%
+  ggplot() +
+  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
+  scale_fill_manual(values=bar_colors) +
+  labs(x="LANDIS Run",
+       y="Total Biomass (kg)",
+       fill="Species") +
+  theme_bw()
+stacked_barchart
+
+ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
+```
+
 ### Plot changes in biomass and age distributions
@@
 
-mapcodes %>%
-  ggplot() +
+mapcodes_vect <- vect(mapcodes, geom=c("X", "Y"), crs="", keepgeom=FALSE)
+
+tree_polys <- list()
+for(i in 1:nrow(mapcodes_vect)){
+  tree_i <- mapcodes_vect[i,]
+  buffer_i <- buffer(tree_i, width = mapcodes_vect$CD_m[i]/2)
+  tree_polys[[i]] <- buffer_i
+}
+mapcodes_poly <- vect(tree_polys)
+writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
+mapcodes_poly <- mapcodes_poly %>%
+  arrange(CD_m) %>%
+  mutate(SpeciesName = case_when(SPECIES_SYMBOL=="PITA" ~ "Loblolly Pine",
+                                 SPECIES_SYMBOL=="PIPA2" ~ "Longleaf Pine",
+                                 SPECIES_SYMBOL=="PIEL" ~ "Slash Pine",
+                                 SPECIES_SYMBOL=="LIST2" ~ "Tulip Poplar",
+                                 SPECIES_SYMBOL=="ACRU" ~ "Red Maple",
+                                 TRUE ~ "Other")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "Other",
+                                "Red Maple",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine",
+                                "Tulip Poplar"
+                              )))
+
+new_colors <- colorblind_pal()(8)[c(1,4,5,6,8)]
+example_mapcode <- ggplot() +
   geom_hline(yintercept = 600, linetype = "dashed") +
   geom_vline(xintercept = 200, linetype = "dashed") +
-  geom_point(aes(X,Y,color=SPECIES_SYMBOL,size=DBH), shape=16) +
-  scale_color_colorblind() +
-  coord_equal() +
-  labs(X = "X (m)",
-       Y = "Y (m)",
-       color = "Species") +
+  geom_spatvector(data=mapcodes_poly, aes(fill=SpeciesName, color=SpeciesName), alpha=0.7) +
+  scale_fill_manual(values = new_colors) +
+  scale_color_manual(values = new_colors) +
+  labs(x = "X (m)",
+       y = "Y (m)",
+       fill = "Species",
+       color="Species") +
   theme_bw()
+example_mapcode
+ggsave("example_mapcode.jpg",path = here("Plots"), height=6)
+
 #TODO: Replace species codes with species names

### 2024-05-30 Manuscript_Figures.Rmd
Create example LANDIS mapcodes, fix mapcode mismach

--- 2024-05-29 Manuscript_Figures.Rmd
@@
 ```{r}
-IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
+IC_tif <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
+IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","output-community-0.img"))
+crs(IC_map) <- crs(IC_tif)
+ext(IC_map) <- ext(IC_tif)
+
+FB_shp <- vect(here("FtBraggBoundary","FtBraggBoundary.shp"))
+FB_shp <- project(FB_shp, IC_map)
+FB_shp <- crop(FB_shp, IC_map)
+
 IC_file <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-0.csv"))
@@
 IC_map_df <- as.data.frame(IC_map) %>%
-  rename(MapCode = IC_Map_FortBragg)
-IC_map_dom <- left_join(IC_map_df, IC_dom)
+  rename(MapCode = Layer_1)
+IC_map_dom <- left_join(IC_map_df, IC_dom) %>%
+  mutate(SpeciesName = case_when(is.na(SpeciesName) ~ "Non-Forest",
+                                 TRUE ~ SpeciesName)) %>%
+  mutate(SpeciesID = case_when(SpeciesName=="Non-Forest" ~ 9,
+                               TRUE ~ SpeciesID))
+
+sp_names <- c(
+  "Oak spp.",
+  "Sweetgum",
+  "Red Maple",
+  "Slash Pine",
+  "Loblolly Pine",
+  "Longleaf Pine",
+  "Shortleaf Pine",
+  "Tulip Poplar",
+  "Non-Forest"
+)
+
 IC_map_rst <- IC_map_dom %>% select(SpeciesID)
-mapcodes <- unique(IC_map_dom$SpeciesID)
-sp_names <- unique(IC_map_dom$SpeciesName)
-IC_levels <- tibble("id"=mapcodes, "levels"=sp_names) %>% drop_na()
 IC_map$IC_map_rst <- IC_map_rst
 IC_dom_map <- IC_map$IC_map_rst
-levels(IC_dom_map) <- IC_levels
+IC_dom_map <- IC_dom_map %>% mutate(IC_map_rst = factor(IC_map_rst, labels = sp_names))
+IC_dom_map <- mask(IC_dom_map, FB_shp)
 ```
@@
 ```{r}
+bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
+  project(crs(IC_dom_map))
+map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
 ggplot() +
   geom_spatraster(data=IC_dom_map) +
-  scale_fill_colorblind() +
+  geom_spatvector(data=bp4, fill=NA, color = "red", linewidth = 0.75) +
+  scale_fill_manual(values=map_colors, na.value = NA) +
   labs(fill="Dominant Tree Species") +
   theme_bw()
-#TODO: Reorder legend, remove NA
+ggsave("IC_map.jpg", path=here("Plots"), width = 7, height = 3)
 ```
@@
 IC_map_df <- as.data.frame(IC_map) %>%
-  rename(MapCode = IC_Map_FortBragg)
+  rename(MapCode = Layer_1)
 IC_df <- BA_split %>% select(MapCode,IC_ID)
@@
 
+### Stacked bar chart of species composition in burn plot
+```{r}
+bp_mapcodes <- unique(as.vector(values(crop(IC_map, bp4))))
+BA_plot <- before_after %>% 
+  filter(MapCode %in% bp_mapcodes) %>%
+  group_by(pre_post, SpeciesName) %>%
+  summarize(CohortAge_Avg = mean(CohortAge),
+            CohortBiomass_Sum = sum(CohortBiomass)) %>%
+  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
+                                                "Fire2-Dry",
+                                                "Fire2-Wet",
+                                                "Fire5-Dry",
+                                                "Fire5-Wet"))) %>%
+  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
+                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
+                                 SpeciesName=="SlashPine" ~ "Slash Pine",
+                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
+                                 SpeciesName=="RedMaple" ~ "Red Maple",
+                                 SpeciesName=="SweetGum" ~ "Sweetgum",
+                                 SpeciesName=="WhiteOak" ~ "White Oak",
+                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
+                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "White Oak",
+                                "Turkey Oak",
+                                "Sweetgum",
+                                "Red Maple",
+                                "Shortleaf Pine",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine",
+                                "Tulip Poplar"
+                              )))
+
+bar_colors <- colorblind_pal()(8)[c(2,3,1,4,5,6,8)]
+stacked_barchart <- BA_plot %>%
+  ggplot() +
+  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
+  scale_fill_manual(values=bar_colors) +
+  labs(x="LANDIS Run",
+       y="Total Biomass (kg)",
+       fill="Species") +
+  theme_bw()
+stacked_barchart
+
+ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
+```
+
 ### Plot changes in biomass and age distributions
@@
 treelist <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","Treelist_postlandis_cycle0.csv"))
-set.seed = 14
-sample_mapcode <- sample(unique(treelist$MapCode),1)
-mapcode <- treelist %>% filter(MapCode == sample_mapcode)
 mapcodes <- treelist %>%
@@
 mapcodes_poly <- vect(tree_polys)
-writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"))
-mapcodes_poly <- arrange(mapcodes_poly, CD_m)
+writeVector(mapcodes_poly, here("Plots","sample_mapcode_canopies.shp"), overwrite=T)
+mapcodes_poly <- mapcodes_poly %>%
+  arrange(CD_m) %>%
+  mutate(SpeciesName = case_when(SPECIES_SYMBOL=="PITA" ~ "Loblolly Pine",
+                                 SPECIES_SYMBOL=="PIPA2" ~ "Longleaf Pine",
+                                 SPECIES_SYMBOL=="PIEL" ~ "Slash Pine",
+                                 SPECIES_SYMBOL=="LIST2" ~ "Tulip Poplar", #I know this is actually sweetgum
+                                 SPECIES_SYMBOL=="ACRU" ~ "Red Maple",
+                                 TRUE ~ "Other")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "Other",
+                                "Red Maple",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine",
+                                "Tulip Poplar"
+                              )))
 
+new_colors <- colorblind_pal()(8)[c(1,4,5,6,8)]
 example_mapcode <- ggplot() +
@@
   geom_vline(xintercept = 200, linetype = "dashed") +
-  geom_spatvector(data=mapcodes_poly, aes(fill=SPECIES_SYMBOL, color=SPECIES_SYMBOL), alpha=0.7) +
-  scale_fill_colorblind() +
-  scale_color_colorblind() +
+  geom_hline(yintercept = 700, linetype = "dashed") +
+  geom_vline(xintercept = 100, linetype = "dashed") +
+  geom_hline(yintercept = 500, linetype = "dashed") +
+  geom_vline(xintercept = 300, linetype = "dashed") +
+  geom_spatvector(data=mapcodes_poly, aes(fill=SpeciesName, color=SpeciesName), alpha=0.7) +
+  scale_fill_manual(values = new_colors) +
+  scale_color_manual(values = new_colors) +
   labs(x = "X (m)",
@@
 example_mapcode
-ggsave("example_mapcode.jpg",path = here("Plots"))
+ggsave("example_mapcode.jpg",path = here("Plots"), height=6)
+
+empty_mapcode <- ggplot() +
+  geom_hline(yintercept = 600, linetype = "dashed") +
+  geom_vline(xintercept = 200, linetype = "dashed") +
+  geom_hline(yintercept = 700, linetype = "dashed") +
+  geom_vline(xintercept = 100, linetype = "dashed") +
+  geom_hline(yintercept = 500, linetype = "dashed") +
+  geom_vline(xintercept = 300, linetype = "dashed") +
+  geom_spatvector(data=mapcodes_poly, fill=NA, color=NA) +
+  labs(x = "X (m)",
+       y = "Y (m)") +
+  theme_bw()
+empty_mapcode
+ggsave("empty_mapcode.jpg",path = here("Plots"), height=6)
 
@@
 ```
+
+```{r}
+example_mapcodes <- unique(mapcodes$MapCode)
+community50 <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-50.csv"))
+landis_examples <- community50 %>% filter(MapCode %in% example_mapcodes)
+View(landis_examples)
+
+ex_colors1 <- colorblind_pal()(8)[c(5,6)]
+ex_colors2 <- colorblind_pal()(8)[c(5,6,8)]
+ex_colors3 <- colorblind_pal()(8)[c(1,4,5)]
+ex_colors4 <- colorblind_pal()(8)[c(1,4,5)]
+ex_colors <- list(ex_colors4,ex_colors2,ex_colors3,ex_colors1)
+for(i in 1:length(example_mapcodes)){
+  landis_examples %>%
+  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
+                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
+                                 SpeciesName=="SweetGum" ~ "Tulip Poplar",
+                                 SpeciesName=="SlashPine" ~ "Slash Pine",
+                                 SpeciesName=="RedMaple" ~ "Red Maple")) %>%
+  mutate(SpeciesName = factor(SpeciesName, 
+                              levels = c("Red Maple",
+                                         "Slash Pine",
+                                         "Loblolly Pine",
+                                         "Longleaf Pine",
+                                         "Tulip Poplar")),
+         CohortAge = factor(CohortAge)) %>%
+  filter(MapCode == example_mapcodes[i]) %>%
+  ggplot() +
+    geom_bar(stat="identity", 
+             position=position_dodge2(preserve = "single", padding = 0.2), 
+             aes(x=interaction(CohortAge,SpeciesName,sep="-"),
+                 y=CohortBiomass,
+                 fill=SpeciesName)) +
+    scale_x_discrete(labels = function(x) gsub("-.*","", x),limits=rev) +
+    scale_fill_manual(values = ex_colors[[i]]) +
+    scale_y_continuous(limits = c(0,3800)) +
+    labs(x="Cohort Age",y="Cohort Biomass") +
+    coord_flip() +
+    theme_bw() +
+    theme(legend.position = "none",
+          # axis.title = element_blank(),
+          strip.background = element_blank(),
+          strip.text = element_blank())
+  ggsave(paste0("ex_biomass_",example_mapcodes[i],".jpg"), path=here("Plots"), height=2, width=2.15)
+}
+```

### 2024-06-07 Manuscript_Figures.Rmd
New burn plot

@@
 IC_tif <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","IC_Map_FortBragg.tif"))
-IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","output-community-0.img"))
+IC_map <- rast(here("1.LANDIS-MODEL","LANDIS_run-Fire5-Dry","output-community-0.img"))
 crs(IC_map) <- crs(IC_tif)
@@
 ```{r}
-bp4 <- vect(here("BurnPlots","FB_plot4.shp")) %>%
+bp4 <- vect(here("1.LANDIS-MODEL","Shapefiles","burn_plot.shp")) %>%
   project(crs(IC_dom_map))
@@
 ```{r}
+single_colors <- colorblind_pal()(8)[c(2,5,6)]
 ggplot() +
   geom_spatraster(data=IC_crop_bp4)+
-  scale_fill_colorblind()+
+  scale_fill_manual(values = single_colors)+
   geom_spatvector(data=bp4,fill=NA,linewidth=1)+

### 2024-06-27 Manuscript_Figures.Rmd
Add NoScrapple run

@@
                                  SpeciesName=="SweetGum" ~ "Sweetgum",
-                                 SpeciesName=="WhiteOak" ~ "Oak spp.",
-                                 SpeciesName=="TurkeyOak" ~ "Oak spp.",
+                                 SpeciesName=="WhiteOak" ~ "White Oak",
+                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
                                  SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
@@
                               levels = c(
-                                "Oak spp.",
+                                "Turkey Oak",
+                                "White Oak",
                                 "Sweetgum",
@@
                                  TRUE ~ SpeciesName)) %>%
-  mutate(SpeciesID = case_when(SpeciesName=="Non-Forest" ~ 9,
+  mutate(SpeciesID = case_when(SpeciesName=="Non-Forest" ~ 10,
                                TRUE ~ SpeciesID))
@@
 sp_names <- c(
-  "Oak spp.",
+  "Turkey Oak",
+  "White Oak",
   "Sweetgum",
@@
   project(crs(IC_dom_map))
-map_colors <- c(colorblind_pal()(8)[c(2,3,1,4,5,6,7,8)],"gray70")
+map_colors <- c(colorblind_pal()(8)[2], "green", colorblind_pal()(8)[c(3,1,4,5,6,7,8)],"gray70")
 ggplot() +
@@
 fire5_wet <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-Fire2-Dry","community-input-file-50.csv"))
+noscrpple <- read.csv(here("1.LANDIS-MODEL","LANDIS_run-NoScrapple","community-input-file-50.csv"))
 before$pre_post <- "Initial Conditions"
@@
 fire5_wet$pre_post <- "Fire5-Wet"
-before_after <- rbind(before,fire2_dry,fire2_wet,fire5_dry,fire5_wet)
+noscrpple$pre_post <- "No Scrapple"
+before_after <- rbind(before,fire2_dry,fire2_wet,fire5_dry,fire5_wet,noscrpple)
 ```
@@
                                 "Red Maple",
-                                "Oak spp."
+                                "Turkey Oak"
                               ))) %>%
@@
   rename(F5W_ID = FT_ID) %>%
+  left_join(forest_types, by=join_by("No Scrapple"=="forest_type")) %>%
+  rename(noscrp_ID = FT_ID) %>%
   mutate(IC_ID = as.numeric(IC_ID),
@@
          F5D_ID = as.numeric(F5D_ID),
-         F5W_ID = as.numeric(F5W_ID))
+         F5W_ID = as.numeric(F5W_ID),
+         noscrp_ID = as.numeric(noscrp_ID))
 
@@
 F5W_df <- BA_split %>% select(MapCode,F5W_ID)
+noscrp_df <- BA_split %>% select(MapCode,noscrp_ID)
 
@@
 F5W_map <- left_join(IC_map_df, F5W_df)
+noscrp_map <- left_join(IC_map_df, noscrp_df)
 
@@
 F5W_rst <- F5W_map %>% select(F5W_ID)
+noscrp_rst <- noscrp_map %>% select(noscrp_ID)
 
@@
 IC_map$`Fire5-Wet` <- F5W_rst
+IC_map$`No Scrapple` <- noscrp_rst
 
@@
 F5W_all <- IC_map$`Fire5-Wet`
+noscrp_all <- IC_map$`No Scrapple`
 
@@
 levels(F5W_all) <- forest_types %>% select(FT_ID, forest_type)
-before_after_all <- c(IC_all,F2D_all,F2W_all,F5D_all,F5W_all)
-names(before_after_all) <- c("Initial Conditions","Fire2-Dry","Fire2-Wet","Fire5-Dry","Fire5-Wet")
+levels(noscrp_all) <- forest_types %>% select(FT_ID, forest_type)
+before_after_all <- c(IC_all,F2D_all,F2W_all,F5D_all,F5W_all,noscrp_all)
+names(before_after_all) <- c("Initial Conditions","Fire2-Dry","Fire2-Wet","Fire5-Dry","Fire5-Wet","No Scrapple")
 ```
@@
                                                 "Fire5-Dry",
-                                                "Fire5-Wet"))) %>%
+                                                "Fire5-Wet",
+                                                "No Scrapple"))) %>%
   mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
@@
 
-bar_colors <- colorblind_pal()(8)[c(2,3,1,4,5,6,8)]
+bar_colors <- colorblind_pal()(8)[c(2,5,6,4,5,6,8)]
 stacked_barchart <- BA_plot %>%
   ggplot() +
-  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum, fill=SpeciesName)) +
+  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum/1000, fill=SpeciesName)) +
   scale_fill_manual(values=bar_colors) +
   labs(x="LANDIS Run",
-       y="Total Biomass (kg)",
+       y="Total Biomass (metric tons)",
        fill="Species") +

### 2024-06-27 DRM_framework_coupling.py

@@ -494,8 +494,8 @@ def main():
 
     nfuel = 2  # number of tree species (if not using LANDIS)
 
-    MAKE_CLEAN = False
-    RUN_LANDIS = False
+    MAKE_CLEAN = True
+    RUN_LANDIS = True
 
     # Build Trees
     os.chdir("5.TREES-QUICFIRE")

### 2024-06-27 analyze_data.R

@@ -45,8 +45,10 @@ dat_summ_clean <- dat_summ_sd %>%
                          "total_canopy_cons_pct",
                          "average_max_power",
                          "average_res_time_power")) %>%
-  mutate(Rotation = if_else(Rotation== "Fire2", "2-Year", "5-Year"),
-         Climate = if_else(Climate=="Dry", "Hot-Dry", "Hot-Wet"))
+  mutate(Rotation = case_when(Rotation == "Fire2" ~ "2-Year", 
+                              Rotation == "Fire5" ~ "5-Year",
+                              TRUE ~ "No Rx Fire"),
+         Climate = if_else(Climate=="Dry" | is.na(Climate), "Hot-Dry", "Hot-Wet"))
 
 my_colors = colorblind_pal()(8)[2:8]
 
@@ -57,7 +59,7 @@ dat_cons <- dat_summ_clean %>%
                               variable=="total_canopy_cons_pct" ~ "Total Canopy\nConsumption (%)"))
 
 consumption_plot <- dat_cons %>% ggplot() +
-  geom_bar(stat="identity",aes(Rotation,value, fill=Climate),position=position_dodge()) +
+  geom_bar(stat="identity",aes(Rotation,value, fill=Climate),position=position_dodge2(preserve="single")) +
   facet_wrap(.~variable, scales="free_y") +
   scale_fill_manual(values = my_colors) +
   labs(x = "Fire Rotation",

### 2024-06-27 analyze_quicfire.py

@@ -132,7 +132,7 @@ def get_max_reaction_rate(sim: SimulationOutputs, arrpath: Path, plot: bool = Tr
 HERE = Path(__file__).parent
 runs_dir = HERE / "7.QUICFIRE-MODEL" / "projects"
 
-runs = ["Fire2-Dry", "Fire5-Dry", "Fire2-Wet", "Fire5-Wet"]
+runs = ["Fire2-Dry", "Fire5-Dry", "Fire2-Wet", "Fire5-Wet", "NoScrapple"]
 for run in runs:
     runpath = runs_dir / run
     quic_fire = QUIC_fire.from_file(runpath, version="v5")

### 2024-06-27 qf_outputs_to_dataframe.R

@@ -18,7 +18,7 @@ output_to_rst <- function(output, out_arr, plot_bounds){
 }
 
 #### ASSEMBLE DATASET ####
-runs <- c("Fire2-Dry","Fire5-Dry","Fire2-Wet","Fire5-Wet")
+runs <- c("Fire2-Dry","Fire5-Dry","Fire2-Wet","Fire5-Wet","NoScrapple")
 outputs <- c("mass_burnt_pct",
              "surface_consumption",
              "surface_consumption_pct",
@@ -37,7 +37,7 @@ burn_plot <- vect(here("1.LANDIS-MODEL",
                          "burn_plot.shp"))
 
 for(run in runs){
-  run_df = data.frame("Run" = rep(run,90000))
+  run_df = data.frame("Run" = rep(run,89700))
   for(output in outputs){
     out_arr <- read.table(here("7.QUICFIRE-MODEL",
                                "projects", 
@@ -57,5 +57,5 @@ for(run in runs){
 
 
 
-all_data <- bind_rows(`Fire2-Dry_df`, `Fire2-Wet_df`, `Fire5-Dry_df`, `Fire5-Wet_df`)
+all_data <- bind_rows(`Fire2-Dry_df`, `Fire2-Wet_df`, `Fire5-Dry_df`, `Fire5-Wet_df`, NoScrapple_df)
 write.csv(all_data, here("all_data.csv"), row.names = F)

### 2024-06-27 9.FIA/FIA_age_regression.py
Cosmetic updates and minor fixes

@@ -2,11 +2,11 @@
 """
 Created on Fri Sep 30 15:59:20 2022
 
-@author: FireScience
+@author: Niko Tutland
 """
 
 import pandas as pd
-import os
+from pathlib import Path
 import numpy as np
 import pickle
 import matplotlib.pyplot as plt
@@ -15,151 +15,208 @@ from sklearn.model_selection import train_test_split
 from sklearn.metrics import r2_score
 from skranger.ensemble import RangerForestRegressor
 
+
 def main():
     ## User inputs ########
-    fia_path = os.path.abspath("C://Users/FireScience/Documents/2022_Projects/landis_quicfire/Landis_to_Treelist/FIA_raw") #where are the raw FIA data located?
-    out_path = os.path.abspath("C://Users/FireScience/Documents/2022_Projects/landis_quicfire/Landis_to_Treelist/RF_models") #where do you want the model objects saved?
-    plot_path = os.path.abspath("C://Users/FireScience/Documents/2022_Projects/landis_quicfire/Landis_to_Treelist/RF_models/Plots") #where do you want the plots saved?
-    fia_done = True # has an FIA_all file already been made?
+    fia_path = Path(__file__).parent / "FIA_raw"  # where are the raw FIA data located?
+    out_path = (
+        Path(__file__).parent / "RF_Models"
+    )  # where do you want the model objects saved?
+    plot_path = out_path / "Plots"  # where do you want the plots saved?
+    plot_path.mkdir(exist_ok=True)
+    fia_done = False  # has an FIA_all file already been made?
     ## End user inputs ####
-    
+
     ## Use 11 states from western USFS Regions that measure tree age
-    states = ["WA","OR","CA","ID","NV","UT","AZ","NM","CO","WY","MT"]
-    
+    states = ["WA", "OR", "CA", "ID", "NV", "UT", "AZ", "NM", "CO", "WY", "MT"]
+
     ## Compile all FIA data from Rocky Mountain and Pacific Northwest research stations
-    FIA_all = compile_fia(fia_done,fia_path,states,out_path)
-    
+    FIA_all = compile_fia(fia_done, fia_path, states, out_path)
+
     ## Fit random forest models for each major species group
-    # fit_rf(FIA_all,out_path,group=1,prop=0.5)
-    fit_rf(FIA_all,out_path,plot_path,group=2,prop=0.2)
-    # fit_rf(FIA_all,out_path,3)
-    # fit_rf(FIA_all,out_path,4)
-    
[…]

### 2024-12-13 9.FIA/FIA_age_regression.py
Evaluate final model using k-fold cross-validation

@@ -11,7 +11,7 @@ import numpy as np
 import pickle
 import matplotlib.pyplot as plt
 from sklearn.model_selection import RandomizedSearchCV
-from sklearn.model_selection import train_test_split
+from sklearn.model_selection import KFold
 from sklearn.metrics import r2_score, root_mean_squared_error
 from skranger.ensemble import RangerForestRegressor
 
@@ -36,8 +36,8 @@ def main():
     ## Fit random forest models for each major species group
     fit_rf(FIA_all, out_path, plot_path, group=1, prop=0.5)
     fit_rf(FIA_all, out_path, plot_path, group=2, prop=0.2)
-    fit_rf(FIA_all, out_path, plot_path, 3)
-    fit_rf(FIA_all, out_path, plot_path, 4)
+    # fit_rf(FIA_all, out_path, plot_path, 3)
+    # fit_rf(FIA_all, out_path, plot_path, 4)
 
     ##### End main function
 
@@ -59,16 +59,12 @@ def fit_rf(
     FIA_reg["physclcd"] = FIA_reg["physclcd"].astype(
         "category"
     )  # make sure physiognomic class is a categorical variable
-    x_train, x_test, y_train, y_test = (
-        train_test_split(  # split the data into training and test sets
-            FIA_reg.drop(
-                ["AGE"], axis="columns"
-            ),  # define predictors by dropping response
-            FIA_reg["AGE"],  # define response
-            test_size=0.2,  # put 20% of the data into the test set
-            random_state=1995,
-        )
-    )
+
+    # Get predictors and response
+    x_all = FIA_reg.drop(["AGE"], axis="columns")  # predictors for whole dataset
+    y_all = FIA_reg["AGE"]  # response for whole dataset
+
+    print("Tuning hyperparameters...")
     tune_spec = RangerForestRegressor(  # specify the model used for tuning
         seed=47, n_estimators=500  # set seed  # use 500 trees
     )
@@ -91,54 +87,77 @@ def fit_rf(
         n_jobs=8,  # use parallel processing
         scoring="neg_root_mean_squared_error",  # choose best parameters based on lowest RMSE
     )
-    print("Tuning hyperparameters...")
-    tune_res.fit(x_train, y_train)  # do the cross-validation
+    tune_res.fit(x_all, y_all)  # do the cross-validation
[…]

### 2024-12-13 Manuscript_Figures.Rmd
Plot biomass of small trees

@@
 library(sf)
+library(patchwork)
 ```
@@
                                                 "Fire5-Wet",
-                                                "No Scrapple"))) %>%
+                                                "No Scrapple"),
+                           labels = c("Initial Conditions",
+                                      "Fire2-Dry",
+                                      "Fire2-Wet",
+                                      "Fire5-Dry",
+                                      "Fire5-Wet",
+                                      "NoFire-Wet"))) %>%
   mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
@@
 ggsave("biomass_barchart.jpg",path = here("Plots"), height=4)
+```
+
+```{r}
+BA_plot_small <- before_after %>% 
+  filter(MapCode %in% bp_mapcodes) %>%
+  filter(CohortAge < 50) %>%
+  group_by(pre_post, SpeciesName) %>%
+  summarize(CohortAge_Avg = mean(CohortAge),
+            CohortBiomass_Sum = sum(CohortBiomass)) %>%
+  mutate(pre_post = factor(pre_post, levels = c("Initial Conditions",
+                                                "Fire2-Dry",
+                                                "Fire2-Wet",
+                                                "Fire5-Dry",
+                                                "Fire5-Wet",
+                                                "No Scrapple"),
+                           labels = c("Initial Conditions",
+                                      "Fire2-Dry",
+                                      "Fire2-Wet",
+                                      "Fire5-Dry",
+                                      "Fire5-Wet",
+                                      "NoFire-Wet"))) %>%
+  mutate(SpeciesName = case_when(SpeciesName=="LobPine" ~ "Loblolly Pine",
+                                 SpeciesName=="LongleafPine" ~ "Longleaf Pine",
+                                 SpeciesName=="SlashPine" ~ "Slash Pine",
+                                 SpeciesName=="TulipTree" ~ "Tulip Poplar",
+                                 SpeciesName=="RedMaple" ~ "Red Maple",
+                                 SpeciesName=="SweetGum" ~ "Sweetgum",
+                                 SpeciesName=="WhiteOak" ~ "White Oak",
+                                 SpeciesName=="TurkeyOak" ~ "Turkey Oak",
+                                 SpeciesName=="ShortPine" ~ "Shortleaf Pine")) %>%
+  mutate(SpeciesName = factor(SpeciesName,
+                              levels = c(
+                                "White Oak",
+                                "Turkey Oak",
+                                "Sweetgum",
+                                "Red Maple",
+                                "Shortleaf Pine",
+                                "Slash Pine",
+                                "Loblolly Pine",
+                                "Longleaf Pine",
+                                "Tulip Poplar"
+                              )))
+
+bar_colors <- colorblind_pal()(8)[c(2,5,6,4,5,6,8)]
+smalltrees_barchart <- BA_plot_small %>%
+  ggplot() +
+  geom_bar(stat="identity",aes(pre_post,CohortBiomass_Sum/1000, fill=SpeciesName)) +
+  scale_fill_manual(values=bar_colors) +
+  labs(x="LANDIS Run",
+       y="Total Biomass (metric tons)",
+       fill="Species") +
+  theme_bw()
+smalltrees_barchart
+
+ggsave("biomass_smalltrees_barchart.jpg",path = here("Plots"), height=4)
+```
+
+```{r}
+biomass <- (stacked_barchart / smalltrees_barchart +
+  plot_layout(guides = "collect", axes = "collect") &
+  theme(legend.position = "bottom",
+        plot.tag.position = c(0.13,0.95))) +
+  plot_annotation(tag_levels = "A")
+
+# biomass
+ggsave("biomass_barcharts.jpg", path = here("Plots"), height = 8, width = 5.1)
 ```

### 2024-12-13 analyze_data.R

@@ -195,6 +195,11 @@ ccsp %>%
        color="Scenario") +
   theme_bw()
 
+ccsp %>%
+  filter(strata > 4) %>%
+  group_by(run) %>%
+  summarize(sum_consump = sum(canopy_consumption_strata))
+
 runs <- c("Fire2-Dry","Fire5-Dry","Fire2-Wet","Fire5-Wet")
 spline_list <- list()
 for(i in 1:length(runs)){

### 2024-12-13 RF_validation_plots.R
Create RF_validation_plots.R

@@ -1,0 +1,93 @@
+library(here)
+library(tidyverse)
+library(ggthemes)
+library(tidymodels)
+
+spgrps <- c(1,2,3,4)
+
+df_list <- list()
+for(i in 1:length(spgrps)){
+  metrics <- read.csv(here("9.FIA","RF_Models","Plots",paste0("cv_metrics_spgrp",spgrps[i],".csv")))
+  metrics$spgrp <- factor(spgrps[i])
+  df_list[[i]] <- metrics
+}
+
+metrics <- bind_rows(df_list)
+  
+metrics %>% 
+  rename(`R-squared` = R2) %>%
+  pivot_longer(cols = c("RMSE","R-squared"),
+               names_to = "metric",
+               values_to = "value") %>%
+  mutate(spgrp = factor(spgrp, levels = c(1,2,3,4),
+                        labels = c("Pines","Other Conifers","Soft Hardwoods","Hard Hardwoods"))) %>%
+  ggplot() +
+  geom_boxplot(aes(spgrp,value,color=spgrp)) +
+  geom_jitter(aes(spgrp,value,color=spgrp, fill=spgrp), width=0.2, shape=21, alpha=0.5) +
+  facet_wrap(.~metric, scales="free_x") +
+  scale_color_colorblind() +
+  scale_fill_colorblind() +
+  scale_x_discrete(limits=rev) +
+  labs(x="Species Group",
+       y="RMSE") +
+  coord_flip() +
+  theme_bw() +
+  theme(legend.position = "none",
+        axis.title.x = element_blank())
+
+ggsave("model_metrics.png", path=here("9.FIA","RF_Models","Plots"), width=7, height=1.8)
+
+##
+df_list <- list()
+for(i in 1:length(spgrps)){
+  preds <- read.csv(here("9.FIA","RF_Models","Plots",paste0("cv_predictions_spgrp",spgrps[i],".csv")))
+  preds$spgrp <- factor(spgrps[i])
+  df_list[[i]] <- preds
+}
+preds <- bind_rows(df_list)
+
+preds <- preds %>%
+  mutate(age_class = case_when(y_test < 50 ~ "< 50",
+                               y_test < 100 ~ "50-100",
+                               y_test < 150 ~ "100-150",
+                               y_test < 200 ~ "150-200",
+                               TRUE ~ "200+")) %>%
[…]
